---
title: "data_wrangling_ii"
author: "Priyal"
date: "10/11/2018"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(rvest)
library(httr)

```


## Scrape a table

```{r}
url = "http://samhda.s3-us-gov-west-1.amazonaws.com/s3fs-public/field-uploads/2k15StateFiles/NSDUHsaeShortTermCHG2015.htm"

drug_use_xml = read_html(url)

```

Get the tables from the html

All the objects labelled as table will be extracted.
```{r}
drug_use_xml %>%
  html_nodes(css = "table")
```

We have extracted 15 tables. 

Extracting 1st table using square brackets.

```{r}
drug_use_xml %>%
  html_nodes(css = "table") %>%
  .[[1]] %>% 
  html_table() %>%
  slice(-1) %>% 
  as_tibble()
```

Slice was used to remove the first row.

##Learning Assessment

```{r Learning Assesment}

url = "https://www.bestplaces.net/cost_of_living/city/new_york/new_york"

cost_of_living_ny = read_html(url)

```


```{r}
 cost_of_living_ny %>%
  html_nodes(css = "table") %>% 
  .[[1]] %>% 
  html_table(header = TRUE) 
```

##CSS Selectors

The information on the Harry Potter Saga page from IMDB does not exist in the form of table. Use Selector Gadget.

```{r}
title_saga = read_html("https://www.imdb.com/list/ls000630791/") %>% 
  html_nodes(css = ".lister-item-header a") %>% 
  html_text()

gross_rev = read_html("https://www.imdb.com/list/ls000630791/") %>% 
  html_nodes(css = ".text-small:nth-child(7) span:nth-child(5)") %>% 
  html_text()

hp_saga_df = tibble(title = title_saga, rev = gross_rev)

```


```{r}
url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=1"

dynamite_html = read_html(url)
review_titles = dynamite_html %>%
  html_nodes("#cm_cr-review_list .review-title") %>%
  html_text()

review_stars = dynamite_html %>%
  html_nodes("#cm_cr-review_list .review-rating") %>%
  html_text()

review_text = dynamite_html %>%
  html_nodes(".review-data:nth-child(4)") %>%
  html_text()

review_df = tibble(
  stars = review_stars,
  title = review_titles,
  text = review_text
  )


```


##APIs

Get the water data

Here we have used; API--> CSV

```{r}
nyc_water = GET("https://data.cityofnewyork.us/resource/waf7-5gvc.csv") %>% 
content("parsed")
```

Using API--> JSON
It gives you more information than just the rectangle you extracted with CSV
```{r}
nyc_water = GET("https://data.cityofnewyork.us/resource/waf7-5gvc.json") %>% 
  content("text") %>% 
   jsonlite::fromJSON() %>% 
  as_tibble()
```


